Reading Notes

### 2020-08-26 2pd.tex
objective 1 edit, c g to c-g'd

For this research we propose to develop a flexible method for specifying coarse grain models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.

@@

%%create models for new opv compounds>
In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse grain models.
A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse grain elements. %% reword?

%%gain insight into the limits of coarse graining>
The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse grain models.
Currently there is no agreed-upon ``best'' scheme for a coarse grain mapping operator.
By making a simple and easy-to-use coarse graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
%% What is the minimum structure needed to represent a complex molecule? %% reword? omit?

@@

Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse grain site.
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
%%<how do cg models let us access long length/time??>
Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
The heart of coarse graining is the removal of degrees of freedom. 
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse grain models are ideal for examining polymer properties\cite{Gartner2019a}.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

The resolution of coarse grain systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
%%<examples of cg models and the cool things they do>
General coarse grain models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
A coarse grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
%% transition?
Which model is right depends on the length and time scale on which the property of interest can be observed.

%%<multiscale sims>
For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5--10 nm)\cite{Huang2010}; it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
%%<what stands in our way?>

@@

%%<segue from automated creation of forcefields to...>
%%<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse grain site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse grain system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend? What groups have the most dominant interactions in this structure). %%<cite any model where rings are one site><cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
%%<how cg potentials have been attained> 
Deciding on a mapping operator is one part of creating a coarse grain model, the second step is to create an effective potential for the site.

@@

%% TODO
%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps. I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process. Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
There are numerous methods for deriving coarse grain potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
%%<IBI>
IBI is where a coarse grain potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item 
        The coarse grain system is mapped onto an equilibrated atomistic one.

@@

The coarse grain potential derived from IBI is not transferrable to different thermodynamic statepoints.
This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
There are many attempts to create transferrable CG potentials, for example:
The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
%%<so we probably want to create our own potentials>
%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.>~\cite{Moore2014}

@@

%%<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
%%<how morphct pipeline would work: cg-backmap-ct>
MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse grain morphology.
%% MorphCT has some built in backmapping tools which use an xml file, but  (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
%%<making morphct more modular to allow it to be used in a workflow not cli>

@@

My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
% With lan - About excitonic splitting, using DFT, DNA. 
An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI\@.
These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
    \caption{Hexane chemical structure (top) overlaid with coarse grain mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
\end{wrapfigure}

@@

For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).

@@

%%\begin{wrapfigure}{L}{0.5\linewidth}
%%    \centering
%%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
%%    \caption{XML file used by VOTCA to specify a three site coarse grain mapping of n-hexane}
%%    \label{hexanexml}
%%\end{wrapfigure}

It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse grain sites (A-B-A), that the process will also be simple.
In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
To explain, let's discuss my proposed alternative:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
The mapping here is specified as a list of site name SMARTS string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}). % chktex 18
The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first. % chktex 18
The bonding and angles of the resulting coarse grain sites can then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
(\autoref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol

We propose a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.%%<cite openbabel,SMILES, SMARTS>
This pattern matching is also implemented in the Openbabel package.
If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
%% another application?
This mapping scheme could even be used to make the mapping process easier for established coarse grain models.
It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
This could make parameterizing new compounds for an existing method more foolproof.

@@

My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
Once we have a tabulated coarse grain force field, we can create a larger simulation using our coarse grain model.
Finally, once we have an equilibrated coarse grain trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.

>>>>

For this research we propose to develop a flexible method for specifying coarse-grained models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolutiuon e.g., charge transport calculations.
This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may even be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
A poly-3-hexylthiophene (P3HT):NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM\cite{Baran2017}.
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.%%<there aren't a lot of cg models that already exist for these new compounds>
It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.

@@

%%create models for new opv compounds>
In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?

%%gain insight into the limits of coarse graining>
The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
By making a simple and easy-to-use coarse graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
%% What is the minimum structure needed to represent a complex molecule? %% reword? omit?

@@

Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
%%<how do cg models let us access long length/time??>
Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
The heart of coarse graining is the removal of degrees of freedom. 
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

The resolution of coarse-grained systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
%%<examples of cg models and the cool things they do>
General coarse-grained models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
A coarse-grained model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
%% transition?
Which model is right depends on the length and time scale on which the property of interest can be observed.

%%<multiscale sims>
For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5--10 nm)\cite{Huang2010}; it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
In the same way that a coarse-grained model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse-grained structure.
The large length scale, polymer level properties can be equilibrated during the coarse-grained simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.
%%<what stands in our way?>

@@

%%<segue from automated creation of forcefields to...>
%%<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse-grained system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend? What groups have the most dominant interactions in this structure). %%<cite any model where rings are one site><cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
%%<how cg potentials have been attained> 
Deciding on a mapping operator is one part of creating a coarse-grained model, the second step is to create an effective potential for the site.

@@

%% TODO
%% feedback from chris: Also, in the MSIBI section you could take a paragraph or 2 to define what an RDF is, what a Boltzman inverse is, what a potential mean force is, then go into the algorithm steps. I feel like defining those terms in a more general sense would be a good preface to describing the actual approach/steps used in the process. Also, one other question that popped up is how bonds and angles between coarse beads are handled in the MSIBI step.
There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
%%<IBI>
IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item 
        The coarse-grained system is mapped onto an equilibrated atomistic one.

@@

The coarse-grained potential derived from IBI is not transferrable to different thermodynamic statepoints.
This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
There are many attempts to create transferrable CG potentials, for example:
The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.
%%<so we probably want to create our own potentials>
%%<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.>~\cite{Moore2014}

@@

%%<I DONT WANT TO FOCUS ON THIS TOO MUCH. It's only here as a rationale for why backmapping>
%%<how morphct pipeline would work: cg-backmap-ct>
MorphCT, a software previously developed by our lab, can simulate charge transport through an OPV morphology using kinetic Monte Carlo\cite{Miller2018a,MorphCT,morphct2.2}.
The kinetic Monte Carlo algorithm used by MorphCT uses the semi-empirical Zerner's Intermediate Neglect of Differential Overlap (ZINDO/S) quantum chemical calculation to obtain the molecular energy levels of chromophores in the morphology.
The HOMO levels of each chromophore site and the energy splitting induced in the chromophore pairs is used in the Marcus equation to calculate the charge hopping rate between pairs.
A Monte Carlo simulation can then be run using these hopping rates to calculate the movement of charges through the system.
Because this is a quantum chemical calculation, the position of each atom is needed; therefore, a backmapping process is required to calculate the charge transport in a coarse-grained morphology.
%% MorphCT has some built in backmapping tools which use an xml file, but  (which i will discuss why these are bad in the next section) and the package is bulky/CLI/hard-to-use...
%%<making morphct more modular to allow it to be used in a workflow not cli>

@@

My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
% With lan - About excitonic splitting, using DFT, DNA. 
An investigation of the excitonic splitting observed in cyanine dye dimers was done using density functional theory (DFT)\cite{Fothergill2018}.
By comparing calculated with experimental absorption spectra it was found that the solvent may play a large role in the dimer formation and peak shifting.
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes was done using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce an existing model; a task which should be very straightforward in a computational field but which any computational scientist can attest is far from simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \textit{requiring} use of the GUI\@.
These prior works, although not directly related to OPVS or coarse-grained models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
\end{wrapfigure}

@@

For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
In the following example we will take a hexane molecule and map it to three coarse-grained sites (two carbon atoms per site).

@@

%%\begin{wrapfigure}{L}{0.5\linewidth}
%%    \centering
%%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
%%    \caption{XML file used by VOTCA to specify a three site coarse-grained mapping of n-hexane}
%%    \label{hexanexml}
%%\end{wrapfigure}

It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse-grained sites (A-B-A), that the process will also be simple.
In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
To explain, let's discuss my proposed alternative:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA.%%<link to grits>
The mapping here is specified as a list of site name SMARTS string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}). % chktex 18
The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first. % chktex 18
The bonding and angles of the resulting coarse-grained sites can then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
(\autoref{hexane-compare} is the output of one such visualization using py3Dmol.) %%cite py3Dmol

We propose a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer\cite{Weininger1988}.
This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.%%<cite openbabel,SMILES, SMARTS>
This pattern matching is also implemented in the Openbabel package.
If we know the SMARTS string for any given CG mapping, we can map the CG site to its center of mass or geometric center.
I have developed a minimum working example of how this can be done and then how the atomistic structure can be recovered.%%<cite grits>
%% another application?
This mapping scheme could even be used to make the mapping process easier for established coarse-grained models.
It could be fairly straightforward to implement a lookup to check if site parameters already exist (e.g., for the MARTINI model) by going through and writing out the SMARTS pattern for each existing site type.
This could make parameterizing new compounds for an existing method more foolproof.

@@

My plan is to create a workflow which builds on existing tools: signac, freud, mbuild, openbabel, and a previously developed msibi package.
This workflow could start with equilibrated atomistic trajectories from multiple statepoints, then use SMARTS strings to map the CG sites to each trajectory and calculate the effective potentials using MSIBI\@.
Once we have a tabulated coarse-grained force field, we can create a larger simulation using our coarse-grained model.
Finally, once we have an equilibrated coarse-grained trajectory, we can using backmapping to regain the atomic positions and do analysese such as radial distribution function (RDF), charge transport, and diffraction.
If this workflow is streamlined, it can be applied to many different compounds allowing for a high-throughput analysis of many potential OPV compounds.
